Open Science, Open Plant Pathology

### 2020-04-20 analysis/paper/paper.Rmd
Add Nature article introducing FAIR data

If steps are followed to make the data FAIR (Findable, Accessible, Interoptable and Reusable) then it will be readable by humans and machines alike this will help support new discoveries and support further research.
In turn sharing data will lead to new citations for your work as other discover and use it.

>>>>

If steps are followed to make the data FAIR (Findable, Accessible, Interoptable and Reusable) [@Wilkinson2016] then it will be readable by humans and machines alike this will help support new discoveries and support further research.
In turn sharing data will lead to new citations for your work as other discover and use it.
